---
name: Dean Marchiori
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BSc(Math)(Medal), MAppStat, MAppFin, AStat
position: Principal Data Scientist | Applied Statistician
phone: 61 400 459 540  
email: dean@wavedatalabs.com.au
www: deanmarchiori.com   
github: deanmarchiori
linkedin: deanmarchiori
headcolor: 20428c
output: vitae::awesomecv
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# About Me   

Principal Data Scientist, Statistician and industry leader with over 10 years experience working in and leading high performance data science teams.

- University Medalist in Mathematics with dual Masters degrees in Statistics and Finance.
- Expert level R programmer, proficient in Python, SQL, C.
- Microsoft Certified Azure Machine Learning Data Science Associate, proficient in Docker, Azure MLOps, CI/CD, Posit Connect.

# Experience
```{r}
tribble(
  ~role, ~company, ~loc, ~dates, ~details,
  "DIRECTOR & PRINCIPAL DATA SCIENTIST", "Wave Data Labs", "Wollongong Australia", "May 2023 - Present", "Independent consultant and contractor in data science, machine learning, applied mathematics and statistical modelling.",
  "DIRECTOR & PRINCIPAL DATA SCIENTIST", "Wave Data Labs", "Wollongong, Australia", "May 2023 - Present", ">$400k projects delivered in 18 months.",
  "DIRECTOR & PRINCIPAL DATA SCIENTIST", "Wave Data Labs", "Wollongong, Australia", "May 2023 - Present", "Implemented projects from design through to Production MLOps deployments with full CI/CD pipelines.",
  "DATA SCIENCE TEAM LEAD / DATA INSIGHTS MANAGER", "Endeavour Energy", "Sydney, Australia", "Apr 2021 - May 2023", "Established, hired and managed Endeavour's first totally greenfield data science team.",
  "DATA SCIENCE TEAM LEAD / DATA INSIGHTS MANAGER", "Endeavour Energy", "Sydney, Australia", "Apr 2021 - May 2023", "Implemented enterprise wide Microsoft Azure Machine Learning & Posit Connect platforms (1000+ staff organisation).",
  "DATA SCIENCE TEAM LEAD / DATA INSIGHTS MANAGER", "Endeavour Energy", "Sydney, Australia", "Apr 2021 - May 2023", "Led over 20 data science projects including peer reviewed scientific publications and mission critical decision support systems.",
  "SENIOR DATA SCIENTIST", "", "Sydney, Australia", "Oct 2019 - Apr 2021", "Bush fire risk modelling on the electricity grid informing the impact of the removal of over 200 hazardous trees.",
  "SENIOR DATA SCIENTIST", "", "Sydney, Australia", "Oct 2019 - Apr 2021", "Vegetation management optimisation to reduce > 5% OPEX on multi-million dollar maintenance budget.",
  "SENIOR DATA SCIENTIST", "", "Sydney, Australia", "Oct 2019 - Apr 2021", "Developed and deployed a machine learning model to predict the impact of severe storms on the electricity grid with >90% accuracy.",
  "SESSIONAL TEACHING ACADEMIC - SCHOOL OF MATHEMATICAL AND PHYSICAL SCIENCES", "Macquarie University", "Sydney, Australia", "Feb 2022 - Sep 2023", "Instructor in Mathematics & Statistics to over 200 students.",
  "HEAD OF DATA SCIENCE", "Internetrix - Acquired by XPON Technologies Group (ASX:XPN)", "Wollongong, Australia", "Mar 2018 - Oct 2019", "Led 2 x research projects with the University of Wollongong SMART Facility totalling > $150k in research funding.",
  "HEAD OF DATA SCIENCE", "Internetrix - Acquired by XPON Technologies Group (ASX:XPN)", "Wollongong, Australia", "Mar 2018 - Oct 2019", "Product development of time series anomaly detection software.",
  "HEAD OF DATA SCIENCE", "Internetrix - Acquired by XPON Technologies Group (ASX:XPN)", "Wollongong, Australia", "Mar 2018 - Oct 2019", "Greenfield development and launch of internal data science consulting practice.",
  "SENIOR STATISTICIAN", "IRT Group", "Wollongong, Australia", "Nov 2016 - Mar 2018", "Unsupervised ML / Clustering / Customer Segmentation for NFP Aged Care Provider.",
  "SENIOR STATISTICIAN", "IRT Group", "Wollongong, Australia", "Nov 2016 - Mar 2018", "Introduced call-centre staffing optimisation model resulting in > 10% OPEX reduction opportunities.",
  "SENIOR STATISTICIAN", "IRT Group", "Wollongong, Australia", "Nov 2016 - Mar 2018", "Developed and piloted the first ever use of AB Testing and experimental design for marketing campaigns.",
  "SENIOR DATA ANALYST", "ANZ Banking Group", "Sydney, Australia", "May 2014 - Oct 2016", "Advanced statistical modelling.",
  "SENIOR DATA ANALYST", "ANZ Banking Group", "Sydney, Australia", "May 2014 - Oct 2016", "Built marketing campaign analysis apps (Shiny).",
  "SENIOR DATA ANALYST", "ANZ Banking Group", "Sydney, Australia", "May 2014 - Oct 2016", "Programming in R, SAS, SQL.",
  "BUSINESS INTELLIGENCE ANALYST", "", "Sydney, Australia", "Oct 2012 - May 2014", "Designed call centre and queuing optimisation methods.",
  "BUSINESS INTELLIGENCE ANALYST", "", "Sydney, Australia", "Oct 2012 - May 2014", "Completed time series analysis.",
  "BUSINESS INTELLIGENCE ANALYST", "", "Sydney, Australia", "Oct 2012 - May 2014", "Implemented major telecommunications technology project.",
  "EQUITIES TRADER", "", "Sydney, Australia", "Jun 2011 - Oct 2012", "Trading domestic and international equities, warrants, managed funds.",
) %>%
  detailed_entries(what = role, when = dates, with = company, why = details)
```


# Education
```{r}
tribble(
  ~degree, ~uni, ~loc, ~dates, ~details,
  "MASTER OF APPLIED STATISTICS", "Macquarie University", "Sydney, Australia", "2020 - 2021", "GPA of 6.87 out of 7",
  "MASTER OF APPLIED STATISTICS", "Macquarie University", "Sydney, Australia", "2020 - 2021", "Awarded Macquarie University Award for Academic Excellence",
  "MASTER OF APPLIED STATISTICS", "Macquarie University", "Sydney, Australia", "2020 - 2021", "Awarded Julian Leslie Prize in Statistics",
  "BACHELOR OF SCIENCE (MATHEMATICS)", "Charles Sturt University", "Bathurst, Australia", "2013 - 2017", "GPA of 6.87 out of 7",
  "BACHELOR OF SCIENCE (MATHEMATICS)", "Charles Sturt University", "Bathurst, Australia", "2013 - 2017", "Awarded Undergraduate University Medal",
  "BACHELOR OF SCIENCE (MATHEMATICS)", "Charles Sturt University", "Bathurst, Australia", "2013 - 2017", "Mathematics Major",
  "BACHELOR OF SCIENCE (MATHEMATICS)", "Charles Sturt University", "Bathurst, Australia", "2013 - 2017", "Statistics Minor",
  "MASTER OF APPLIED FINANCE", "Kaplan Professional", "Sydney, Australia", "2010 - 2013", "Major in Financial Markets and Trading",
  "MASTER OF APPLIED FINANCE", "Kaplan Professional", "Sydney, Australia", "2010 - 2013", "Graduated with Distinction"
) %>%
  detailed_entries(degree, dates, uni, loc, details)
```

# Awards & Achievements

```{r}
tribble(
  ~award, ~from, ~year,
  "Julian Leslie Prize in Statistics- Macquarie University", "", "2021",
  "Macquarie University Award for Academic Excellence - Macquarie University", "", "2021",
  "Placed #8 in Top 25 Analytics Leaders in Australia - IAPA", "", "2019",
  "Undergraduate University Medal - Charles Sturt University", "", "2017",
  "Faculty of Science - Executive Dean's List Award - Charles Sturt University", "", "2017",
  "Faculty of Science - Executive Dean's List Award - Charles Sturt University", "", "2016",
  "Faculty of Science - Executive Dean's List Award - Charles Sturt University", "", "2015",
  "Order of Australia Certificate of Commendation - Council of the Order of Australia", "", "2005",
  "Young Australian of the Year (Shoalhaven) - Aust. Day Council", "", "2005"
) %>%
  brief_entries(award, year, from)
```


# Organisations   
```{r}
tribble(
  ~role, ~company, ~loc, ~dates, ~details,
  "ACCREDITED STATISTICIAN", "Statistical Society of Australia", "Australia", "2025", "Holds the 'Accredited Statistician' professional accreditation",
  "CO-CHAIR", "Statistical Society of Australia", "Australia", "2025", "Co-Chair of the Section for Statistical Computing and Graphics",
  "CHAIR", "Statistical Society of Australia", "Australia", "2025", "Chair of the Data Science and accreditation Working Group",
  "SURF RESCUE LIFESAVER", "Surf Lifesaving NSW", "Wollongong, Australia", "2024", "Bronze Medallion, Advanced Resuscitation, Cert IV Public Safety (Aquatic Rescue)",
  "FIRST RESPONDER", "St John Ambulance Australia (NSW)", "NSW", "2006", "Over 500hrs as front line first responder to medical emergencies",
  "FIRST RESPONDER", "St John Ambulance Australia (NSW)", "NSW", "2006", "Received Order of Australia Commendation and Young Australian of the Year Award (Shoalhaven) for meritorious service",
) %>%
  detailed_entries(role, dates, company, loc, details)
```

